Ad-hoc referential expressions for novel shapes in 4-5 year old children

### 2023-10-16 write-ups/CAMP6/abstract.tex
anonymize and submit!

% The next bit is for reserving sufficient space for authors,
% affiliations, and e-mail address.  No need to change for initial
% anonymous version.  For the final version, replace the
% \toggletrue{anonymous} with \togglefalse{anonymous} to de-anonymize.
\usepackage{etoolbox}
\newtoggle{anonymous}
\togglefalse{anonymous}

@@

\textbf{Results:} 
Children uses a variety of different referential expressions to successfully convey the target to their partner (see Examples on next page). Children were 84\% accurate at selecting the target image, and accuracy was relatively stable over time ($\beta=$0.13 [-.04, .31]; Fig 2A). Children's speed to select a target increased over time ($\beta=$-1.24 [-1.89, -.59]; Fig 2B). Children generally produced short descriptions, and the length of descriptions tended to slightly increase over time ($\beta=$0.11 [-.03, .25]; Fig 2C).

@@

		\smallskip
		a flying person $\bullet$
		a superhero$\bullet$
		somebody jumping $\bullet$ two wings with a square in the back with two feet
		\smallskip

		someone building a funnel $\bullet$
		a server$\bullet$
		a person holding up a plate $\bullet$ a man with one foot and a line and a square and a triangle
		\smallskip

		a crocodile tasting an animal in the water$\bullet$
		a whale$\bullet$
		someone flying a plane without a cover$\bullet$
		a person lying on the ground

>>>>

% The next bit is for reserving sufficient space for authors,
% affiliations, and e-mail address.  No need to change for initial
% anonymous version.  For the final version, replace the
% \toggletrue{anonymous} with \togglefalse{anonymous} to de-anonymize.
\usepackage{etoolbox}
\newtoggle{anonymous}
\toggletrue{anonymous}

@@

\textbf{Results:} 
Children use a variety of different referential expressions to successfully convey the target to their partner (see Examples on next page). Children were 84\% accurate at selecting the target image, and accuracy was relatively stable over time ($\beta=$0.13 [-.04, .31]; Fig 2A). Children's speed to select a target increased over time ($\beta=$-1.24 [-1.89, -.59]; Fig 2B). Children generally produced short descriptions, and the length of descriptions tended to slightly increase over time ($\beta=$0.11 [-.03, .25]; Fig 2C).

@@

		\smallskip
		a flying person $\bullet$
		a superhero $\bullet$
		somebody jumping $\bullet$ two wings with a square in the back with two feet
		\smallskip

		someone building a funnel $\bullet$
		a server $\bullet$
		a person holding up a plate $\bullet$ a man with one foot and a line and a square and a triangle
		\smallskip

		a crocodile tasting an animal in the water $\bullet$
		a whale $\bullet$
		someone flying a plane without a cover $\bullet$
		a person lying on the ground
